Total Score

### 2023-01-31 src/MSAtotal_scores.Rmd
renaming columns

```{r climate risk 50 and proportional weights for others}
weights_climate50_prop <- c(0.18, 0.07, 0.11, 0.07, 0.0, 0.07, 0.50)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50_prop = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

@@

```{r}
sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0")
```

>>>>

```{r climate risk 50 and proportional weights for others}

weights_climate50_prop <- c(0.18, 0.07, 0.11, 0.07, 0.0, 0.07, 0.50)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50_prop = cbsa)#this is just a place holder

@@

```{r rename columns and output to google sheet}
criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk)

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0")
```

```{r}
column_order <- c("real_estate_weighted", "rental_weighted", "financial_weighted", "electricity_weighted", "climate_impact_weighted", "climate_risk_weighted", "health_weighted", "cbsa", "city_msa", "state")

weighted_criteria <- criteria_all %>% 
  rename(real_estate_weighted = real_estate_score,
        rental_weighted = landlord_score,
        financial_weighted = normalized_irr,
        electricity_weighted = normalized_annual_renewable,
        climate_impact_weighted = inverted_n_total_co2,
        climate_risk_weighted = normalized_inverted_climate_risk,
        health_weighted = inverted_n_health_emissions_cost)

weighted_criteria <- weighted_criteria[, column_order]

```{r data viz}

score_tidy <- criteria_all %>% 
  pivot_longer(cols = c(real_estate_score, landlord_score, financial_score:climate_risk),
               names_to = "criteria",
               values_to = "criteria_score") %>% 
  filter(city_msa != "Portland") %>% 
  group_by(city_msa)
